### 2022-11-10 README.Rmd
Modified how do_MSE responds to hsargs for new Meta-rules
Added ENVIRON option to control file. Improved compare_scenarios. NoEWN, but vignettes causing trouble

>>>>

* 2022-11-10 aMSE 0.0.22 now have the capacity to introduce productivity events in specific projection years. This can now be done at sau specific levels. One defines the survivorship of recruits in each selected year and also the survivorship of all post-settlement animals. No changes are needed to one's control file if this option is not being used.

* 2022-11-02 aMSE 0.0.21 added changes to how do_MSE responds to hsargs.
